Artin Group Presentations Arising from Cluster Algebras

### 2014-08-12 Paper.tex
added acknowledgements

>>>>

\section{Acknowledgements}

We would like to thank Gregg Musiker for mentoring this project as well as Emily Gunawan for carefully reading over the paper and suggesting many helpful improvements. Additional thanks goes to Vic Reiner for suggesting the problem.
This research was supported by the RTG grant NSF/DMS-1148634. We thank the University of Minnesota School of Mathematics for hosting us.
